TacticToe: Learning the Game of Tactics

### 2018-02-15 tactictoe_jv.tex
Explain the statement of Example 10

In Example~\ref{ex:cs4}, we demonstrate the capabilities of
\tactictoe on a goal that did not have a proof in \holfour.

\todoi{TG to RK: I am not sure what the count
constant is doing. Feel free to add more examples.}

\begin{example}\label{ex:cs4}
\begin{lstlisting}[language=SMLSmall]
count (n+m) DIFF count n = IMAGE ($+n) (count m)
SRW_TAC [ARITH_ss] [fetch "pred_set" "EXTENSION", EQ_IMP_THM] THEN
Q.EXISTS_TAC `x - n` THEN
SRW_TAC [ARITH_ss] []
\end{lstlisting}
\end{example}

>>>>

In Example~\ref{ex:cs4}, we demonstrate the capabilities of \tactictoe on a goal that was not already proved in the \holfour libraries: that the set of numbers $\{0,...,n+m-1\} \setminus \{0,...,n-1\}$ is the same as the set obtained by adding $n$ to everything in $\{0,...,m-1\}$.

\begin{example}\label{ex:cs4}
\begin{lstlisting}[language=SMLSmall]
count (n+m) DIFF count n = IMAGE ((+) n) (count m)
SRW_TAC [ARITH_ss] [fetch "pred_set" "EXTENSION", EQ_IMP_THM] THEN
Q.EXISTS_TAC `x - n` THEN
SRW_TAC [ARITH_ss] []
\end{lstlisting}
\end{example}

\todoi{TG to RK: Feel free to add more examples.}
